Tidy Data

### 2014-05-09 tidy-data.tex
First round of fixes

\item \code{person}, with three possible values (John, Mary, and Jane),

\item \code{treatment}, with two possible values (a and b), and

@@

The experimental design tells us more about the structure of the observations. In this experiment, every combination of of \code{person} and \code{treatment} was measured, a completely crossed design. The experimental design also determines whether or not missing values can be safely dropped. In this experiment, the missing value represents an observation that should have been made, but wasn't, so it's important to keep it. Structural missing values, which represent measurements that can't be made (e.g. the count of pregnant males) can be safely removed.

@@

\begin{itemize}
  \item column headers are values, not variable names
  \item multiple variables are stored in one column
  \item variables are stored in both rows and columns
  \item multiple types of observational units are stored in the same table
  \item a single observational unit is stored in multiple tables
\end{itemize}

@@

\begin{table}[htbp]
  \centering
  \input{data/pew-raw.tex}
  \caption{The first ten rows of data on income and religion from the Pew Forum. Two columns, \code{\$100-150k} and \code{>150k}, have been omitted} 
  \label{tbl:pew-raw}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \input{data/weather-raw.tex}
  \caption{Original weather dataset.  There is a column for each possible day in the month.  Columns \code{d11} to \code{d31} have been omitted to conserve space.}
  \label{tbl:weather-raw}
\end{table}

@@

  \item \proglang{R} (\code{lm()}): \code{y ~ a + b + c * d}

  \item \proglang{SAS} (\code{PROC GLM}): \code{y = a + b + c + d + c * d}

  \item \proglang{SPSS} (\code{glm}): \code{y BY a b c d / DESIGN a b c d c * d}

  \item \proglang{Stata} (\code{regress}): \code{y a b c\#d}

>>>>

\item \code{person}, with three possible values (John, Mary, and Jane).

\item \code{treatment}, with two possible values (a and b).

@@

The experimental design tells us more about the structure of the observations. In this experiment, every combination of of \code{person} and \code{treatment} was measured, a completely crossed design. The experimental design also determines whether or not missing values can be safely dropped. In this experiment, the missing value represents an observation that should have been made, but wasn't, so it's important to keep it. Structural missing values, which represent measurements that can't be made (e.g., the count of pregnant males) can be safely removed.

@@

\begin{itemize}
  \item Column headers are values, not variable names.
  \item Multiple variables are stored in one column.
  \item Variables are stored in both rows and columns.
  \item Multiple types of observational units are stored in the same table.
  \item A single observational unit is stored in multiple tables.
\end{itemize}

@@

\begin{table}[htbp]
  \centering
  \input{data/pew-raw.tex}
  \caption{The first ten rows of data on income and religion from the Pew Forum. Three columns, \code{\$75-100k}, \code{\$100-150k} and \code{>150k}, have been omitted} 
  \label{tbl:pew-raw}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \input{data/weather-raw.tex}
  \caption{Original weather dataset.  There is a column for each possible day in the month.  Columns \code{d9} to \code{d31} have been omitted to conserve space.}
  \label{tbl:weather-raw}
\end{table}

@@

  \item \proglang{R} (\code{lm()}): \code{y ~ a + b + c * d}.

  \item \proglang{SAS} (\code{PROC GLM}): \code{y = a + b + c + d + c * d}.

  \item \proglang{SPSS} (\code{glm}): \code{y BY a b c d / DESIGN a b c d c * d}.

  \item \proglang{Stata} (\code{regress}): \code{y a b c\#d}.
